\documentclass[letterpaper, 10pt]{extarticle}

\usepackage{hyperref}
\urlstyle{same}
%\usepackage[margin=0.5in]{geometry}
\usepackage[text={7.5in, 9.5in}, centering]{geometry}
\usepackage{tabularx}
\renewcommand\tabularxcolumn[1]{m{#1}}

\usepackage{comment}

%\usepackage[T1]{fontenc}
%\usepackage{fontspec}
%\setmainfont[Ligatures=TeX]{Odile}

\def\name{Matthew D. Sweitzer, Ph.D.}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

\setlength\parindent{0pt}
\setlength{\righthyphenmin}{999}

\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{10pt}
  }
}{
  \end{list}
}

\begin{document}

\begin{center}
{\Large \textbf{\name}}
\end{center}

\vspace{0.5em}

\begin{tabularx}{\textwidth}{lXr}
Phone: & (815) 307-2647 &\\
Email: & \href{mailto:email@matthewsweitzer.com}{email@matthewsweitzer.com} &\\
Website: & \href{https://www.matthewsweitzer.com}{matthewsweitzer.com} &\\
\end{tabularx}

\vspace{0.5em}
\rule{\textwidth}{0.75pt}

%\vspace{1em}
%{\large Overview}

%\vspace{0.5em}
%{\footnotesize
%\rule{0.25in}{0pt}My research focuses on using computational modeling methods to understand how social communication evolves, adapts, and informs over time and in complex systems. My coursework included training in statistical modeling, network analysis, and agent-based simulation methods. My research conducted during my graduate program at Ohio State University used these methods to investigate the dynamics of social network formation and how information and opinions are transmitted across network structures. More recently, my work at Sandia National Laboratories allowed me to develop new skills in machine learning methods, such as reinforcement learning and deep neural networks, as well as transformer models used to identify topics in a corpus of text data.}

\vspace{1em}
{\large Professional Experience}

\vspace{0.5em}
\raggedright
\begin{tabularx}{\textwidth}{Xr}
\textbf{Sandia National Laboratories} -- Machine Intelligence and Visualization\\
\rule{0.75em}{0pt}\textit{Senior Member of Technical Staff} & September 30, 2022 -- \textit{present}\\
\rule{0.75em}{0pt}\textit{Postdoctoral Appointee} & July 30, 2021 -- September 30, 2022\\
\rule{0.75em}{0pt}\textit{Graduate Technical Intern} & July 26, 2019 -- July 30, 2021\\
\vspace{0.5em}
\textbf{Sandia National Laboratories} -- Energy Water System Integration\\
\rule{0.75em}{0pt}\textit{Graduate Technical Intern} & May 6, 2019 -- July 26, 2019\\
\end{tabularx}

\vspace{0.5em}
{\setlength{\tabcolsep}{0.25em}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{>{\small}r>{\small}X}
\rule{0.75em}{0pt}$\bullet$ & Led the development and testing of a new network layout algorithm and analytic measure for testing communicative vibration theory and the prediction of social group stability; predictions tested with random forests and deep neural networks.\\
\rule{0.75em}{0pt}$\bullet$ & Established a natural language processing pipeline incorporating multiple methods and visualized results into a live interactive analysis tool.\\
\rule{0.75em}{0pt}$\bullet$ & Programmed agent-based models of disinformation flow and integrated both reinforcement learning agents and Bayesian hyperparameter optimization.\\
\rule{0.75em}{0pt}$\bullet$ & Presented methods and results at project funding meetings, symposia, and scientific conferences.\\
\end{tabularx}}


\vspace{1em}
{\large Technical Skills}

{\small
\begin{itemize}
\setlength\itemindent{-0.5em}
\item \textit{Programming Languages}:\\Python, R, SQL, Bash, Groovy, Javascript, Rust, HTML, CSS, and \LaTeX
\item \textit{Machine Learning and Data Analytic Methods}:\\pytorch, scikitlearn, ERGM-family and other methods for network analysis and simulation, time-series analysis, and statistical modeling (e.g., regression, Bayes)
\item \textit{Simulation Software}:\\Mesa, Netlogo, Repast, N2A, and Anylogic
\item \textit{High-performance Computing Environments}:\\Distributed batch processing using Slurm, Torque, Weights \& Biases, and Amazon AWS
\item \textit{Other Software/Platforms}:\\Shiny, plotly, oTree, Breadboard, Amazon Mechanical Turk, Matlab, Stata, and SPSS
\end{itemize}
}

\vspace{1em}
{\large Education}

\begin{tabularx}{\textwidth}{lX}
\normalsize \\
2015 -- 2021 & \rule{4em}{0pt}Ohio State University - Columbus\\
& \rule{4em}{0pt}\textit{Ph.D., Communication}\\
& \rule{4em}{0pt}Dissertation:\\
& \rule{5em}{0pt}\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Sweitzer_Dissertation.pdf}{``Selection homophily in dynamic political communication networks:}\\
& \rule{6em}{0pt}\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Sweitzer_Dissertation.pdf}{An interpersonal perspective.''}\\
& \rule{4em}{0pt}Committee: \\
& \rule{5em}{0pt}Dr. Robert Bond (Chair, School of Communication)\\
& \rule{5em}{0pt}Dr. Skyler Cranmer (Political Science)\\
& \rule{5em}{0pt}Dr. William Eveland, Jr. (School of Communication)\\
& \rule{5em}{0pt}Dr. Hillary Shulman (School of Communication)\\
\\
2015 -- 2019 & \rule{4em}{0pt}Ohio State University - Columbus\\
& \rule{4em}{0pt}\textit{M.A., Communication}\\
\\
2008 -- 2012 & \rule{4em}{0pt}University of Missouri - Columbia\\
& \rule{4em}{0pt}\textit{B.A., Communication, with honors}\\
\end{tabularx}

%\vspace{1em}
\pagebreak
{\large Peer-Reviewed Publications}

\begin{itemize}
\setlength\itemindent{-0.5em}
\item \textbf{Sweitzer, M. D.}, Gunda, T., \& Gilligan, J. M. (2023). Water narratives in local newspapers within the United States. \textit{Frontiers in Environmental Science - Water and Wastewater Management, 11}. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Sweitzer2023.pdf}{10.3389/fenvs.2023.1038904}

\item Coronel, J. C., Ott, J., Hubner, A., \textbf{Sweitzer, M. D.}, \& Lerner, S. (2023). How are competitive framing environments transformed by person-to-person communication? An integrated social transmission, content analysis, and eye movement monitoring approach. \textit{Communication Research, 50}(1), 3-29. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Coroneletal2020a.pdf}{10.1177/0093650220903596}

\item Bayer, J. B., \textbf{Sweitzer, M. D.}, Xiang, H., Mohan, S., \& Meyers, E. (2022). Reimagining the personal network: The case of Path. \textit{Social Media \& Society, 8}(3) 1-17. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Bayeretal2022.pdf}{10.1177/20563051221119475}

\item Bond, R. M., \& \textbf{Sweitzer, M. D.} (2022). Political homophily in a large-scale online communication network. \textit{Communication Research, 49}(1), 93-115. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/BondSweitzer2018.pdf}{10.1177/0093650218813655}

\item Shulman, H. C., \textbf{Sweitzer, M. D.}, Bullock, O. M., Coronel, J. C., Bond, R. M., \& Poulsen, S. (2022). Predicting vote choice and election outcomes from ballot wording: The role of processing fluency in low information direct democracy elections. \textit{Political Communication, 39}(5), 652-673. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Shulmanetal2022.pdf}{10.1080/10584609.2022.2092920}

\item Coronel, J. C., Bullock, O. M., Shulman, H. C., \textbf{Sweitzer, M. D.}, Bond, R. M., \& Poulsen, S. (2021). Eye movements predict large-scale voting decisions. \textit{Psychological Science, 32}(6), 836-848. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Coroneletal2021.pdf}{10.1177/0956797621991142}

\item Hubner, A., McKnight, J. M., \textbf{Sweitzer, M. D.}, \& Bond, R. M. (2021). Down to a r/science: Integrating computational approaches to the study of credibility on Reddit. \textit{Computational Communication Research, 3}(1), 91-115. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Hubneretal2021.pdf}{10.5117/CCR2021.1.004.HUBN}

\item Coronel, J. C., Poulsen, S., \& \textbf{Sweitzer, M. D.} (2020). Investigating the generation and spread of numerical misinformation: A combined eye movement monitoring and social transmission approach. \textit{Human Communication Research, 46}(1), 25-54. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Coroneletal2020b.pdf}{10.1093/hcr/hqz012}

\item Holt, L. F., \& \textbf{Sweitzer, M. D.} (2020). More than a black and white issue: Ethnic identity, social dominance orientation, and support for the Black Lives Matter movement. \textit{Self and Identity, 19}(1), 16-31. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/HoltSweitzer2020.pdf}{10.1080/15298868.2018.1524788}

\item Melamed, D., Simpson, B., Harrell, A., Munn, C. W., Abernathy, J., \& \textbf{Sweitzer, M. D.} (2020). Homophily and segregation in cooperative networks. \textit{American Journal of Sociology, 125}(4), 1084-1127. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Melamedetal2020.pdf}{10.1086/708142}

\item \textbf{Sweitzer, M. D.}, \& Shulman, H. C. (2018). The effects of metacognition in survey research: Experimental, cross-sectional, and content-analytic evidence. \textit{Public Opinion Quarterly, 82}(4), 745-768. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/SweitzerShulman2018.pdf}{10.1093/poq/nfy034}

\item Coronel, J. C., \& \textbf{Sweitzer, M. D.} (2018). Remembering political messages in dynamic information environments: Insights from eye movements. \textit{Human Communication Research, 44}(4), 374-398. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/CoronelSweitzer2018.pdf}{10.1093/hcr/hqy006}

\item \hangindent=20pt Shulman, H. C., \& \textbf{Sweitzer, M. D.} (2018). Advancing framing theory: Designing an equivalency frame to improve political information processing. \textit{Human Communication Research, 44}(2), 155-175. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/ShulmanSweitzer2018a.pdf}{10.1093/hcr/hqx006}

\item \hangindent=20pt Shulman, H. C., \& \textbf{Sweitzer, M. D.} (2018). Varying metacognition through public opinion questions: How language can affect political engagement. \textit{Journal of Language and Social Psychology, 37}(2), 224-237. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/ShulmanSweitzer2018b.pdf}{10.1177/0261927X17707557}
\end{itemize}

\vspace{0.3em}
{\large Peer-Reviewed Conference Proceedings}

\begin{itemize}
\setlength\itemindent{-0.5em}
\item Gunda, T., \& \textbf{Sweitzer, M. D.} (2022). A natural language processing tool to support stakeholder engagements during a consent-based siting process. In \textit{International High-Level Radioactive Waste Management Conference Proceedings}. La Grange Park, IL: American Nuclear Society. Retrieved from 

\item Sanchez, D., Hackett, K., \textbf{Sweitzer, M. D.}, \& Gunda, T. (2022). Tag it: A natural language processing approach to enhancing delineation of public comments regarding the consent-based siting process. In \textit{International High-Level Radioactive Waste Management Conference Proceedings}. La Grange Park, IL: American Nuclear Society.

\item Doyle, C., Naugle, A., Bernard, M., Lakkaraju, K., Kittinger, R., \textbf{Sweitzer, M. D.}, \& Rothganger, F. (2020). Group formation theory at multiple scales. In R. Thomson, H. Bisgin, C. Dancy, A. Hyder, \& M. Hussain (Eds.), \textit{Social, Cultural, and Behavioral Modeling, SBP-BRiMS 2020} (pp. 171-181). Springer. doi:\href{https://github.com/Matt-Sweitzer/Papers/blob/master/Doyleetal2020.pdf}{10.1007/978-3-030-61255-9\textunderscore 17}

\item Berkemer, S. J., Cheong, S. L., Edgerton, J., Kogan, M., Laisshram, R., Pacheco, A. R., Shannon, A., \textbf{Sweitzer, M. D.}, \& Wang, X. (2019). A study on public transport mobility flows in Singapore. In \textit{2018 Complex Systems Summer School Proceedings}, (pp. 22). Santa Fe, NM: Santa Fe Institute. Retrieved from \href{https://github.com/Matt-Sweitzer/Papers/blob/master/SFI_CSSS_Proceedings.pdf}{https://wiki.santafe.edu/images/9/9d/Proceedings\textunderscore 2018\textunderscore v2.pdf}

\item Gunda, T., \textbf{Sweitzer, M. D.}, Comer, K. T., Finn, C., Murillo-Sandoval, S., \& Huff, J. (2019). Evolution of water narratives in local U.S. newspapers: A case study of Utah and Georgia. In \textit{2018 Complex Systems Summer School Proceedings}, (pp. 9). Santa Fe, NM: Santa Fe Institute. Retrieved from \href{https://github.com/Matt-Sweitzer/Papers/blob/master/SFI_CSSS_Proceedings.pdf}{https://wiki.santafe.edu/images/9/9d/Proceedings\textunderscore 2018\textunderscore v2.pdf}
\end{itemize}

\vspace{0.3em}
{\large Conference Presentations}

\vspace{1em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small Conference on Data Analysis (CoDA)} & {\small 2023}\vspace{0.25em}\\
\hangindent=1em\rule{1em}{0pt}{\raggedright \small \textit{Detecting effective influence campaigns: Integrated theory-based modeling and data analysis of strategy, persuasion, and action}}\\
\rule{1.25em}{0pt}{\small Naugle, A., Krofcheck, D., Doyle, C., Sorensen, A., \textbf{Sweitzer, M. D.}, \& Link, H.}\vspace{0.5em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Longitudinal Analysis of Public Input for Consent-Based Siting: A Case Study of Human-Machine Teaming}}\\
\rule{1.25em}{0pt}{\small Gunda, T., Sanchez, D. N., \textbf{Sweitzer, M. D.}, \& Rogers, A. N.}\vspace{0.5em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Predicting action from topic, sentiment, and emotional content of forum posts}}\\
\rule{1.25em}{0pt}{\small Doyle, C., Naugle, A., Krofcheck, D., \textbf{Sweitzer, M. D.}, \& Sorenson, A.}\vspace{0.5em}\\
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small International High-Level Radioactive Waste Management Conference} & {\small 2022}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{A natural language processing tool to support stakeholder engagements during a consent-based siting process}}\\
\rule{1.25em}{0pt}{\small Gunda, T., \& \textbf{Sweitzer, M. D.}}\vspace{0.5em}\\
\hangindent=1em\rule{1em}{0pt}{\raggedright \small \textit{Tag it: A natural language processing approach to enhancing delineation of public comments regarding the consent-based siting process}}\\
\rule{1.25em}{0pt}{\small Sanchez, D., Hackett, K., \textbf{Sweitzer, M. D.}, \& Gunda, T.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\hangindent=0.5em \rule{0.5em}{0pt}{\small International Conference on Social Computing, Behavioral-Cultural Modeling, \& Prediction and Behavior Representation in Modeling and Simulation (SBP-BRiMS)} & {\small 2022}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{A complex, integrative agent-based model of disinformation cascades}}\\
\rule{1.25em}{0pt}{\small \textbf{Sweitzer, M. D.}, Lakkaraju, K., Wiryadinata, S., Lehrer, G., \& Naugle, A.}\\
\rule{1em}{0pt}{\raggedright \small \textit{A simulation test bed for evaluating data analytic predictors of disinformation flow}}\\
\rule{1.25em}{0pt}{\small Lakkaraju, K., \textbf{Sweitzer, M. D.}, Wiryadinata, S., Lehrer, G., \& Naugle, A.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small International Conference on Computational Social Science} & {\small 2022}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Using social simulations to train, test, and evaluate models for social prediction}}\\
\rule{1.25em}{0pt}{\small Lakkaraju, K., Naugle, A., \textbf{Sweitzer, M. D.}, Wiryadinata, S., \& Lehrer, G.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small National Communication Association (NCA) Annual Convention} & {\small 2020}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Retracing the Path of personal network curation into social media}}\\
\rule{1.25em}{0pt}{\small Bayer, J. B., \textbf{Sweitzer, M. D.}, Xiang, H., Mohan, S., \& Myers, E.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\hangindent=0.5em \rule{0.5em}{0pt}{\small International Conference on Social Computing, Behavioral-Cultural Modeling, \& Prediction and Behavior Representation in Modeling and Simulation (SBP-BRiMS)} & {\small 2020}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Group formation theory at multiple scales}}\\
\rule{1.25em}{0pt}{\small Doyle, C., Naugle, A., Bernard, M., Lakkaraju, K., Kittinger, R., \textbf{Sweitzer, M. D.}, \& Rothganger, F.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small International Conference on Complex Systems (ICCS)} & {\small 2020}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Communicative vibration: A graph-theoretic approach to group stability in an online social network}}\\
\rule{1.25em}{0pt}{\small \textbf{Sweitzer, M. D.}, Kittinger, R., Doyle, C., Naugle, A., Lakkaraju, K., Rothganger, F., \& Verzi, S.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small Association for Education in Journalism and Mass Communication (AEJMC) Annual Conference} & {\small 2020}\vspace{0.25em}\\
\hangindent=1em \rule{1em}{0pt}{\raggedright \small \textit{Transforming science information via person-to-person communication: Insights from experimental transmission chains and eye movements}}\\
\rule{1.25em}{0pt}{\small Hubner, A., Coronel, J. C., Ott, J., \textbf{Sweitzer, M. D.}, \& Lerner, S.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small International Communication Association (ICA) Annual Convention} & {\small 2020}\vspace{0.25em}\\
\hangindent=1em \rule{1em}{0pt}{\raggedright \small \textit{Explaining how people vote on ballot initiatives with language difficulty and metacognition: Results from two ecological experiments}}\\
\rule{1.25em}{0pt}{\small Shulman, H. C., \textbf{Sweitzer, M. D.}, Bullock, O. M., Coronel, J. C., Bond, R. M., \& Poulsen, S.}\vspace{0.5em}\\

\rule{1em}{0pt}{\raggedright \small \textit{Examining how stereotypes cue double-standards for Blacks and women in news}}\\
\rule{1.25em}{0pt}{\small Holt, L. F., \& \textbf{Sweitzer, M. D.}}\vspace{0.5em}\\

\hangindent=1em \rule{1em}{0pt}{\raggedright \small \textit{Thinking reflectively or intuitively: How cognitive reflection moderates the effect of language complexity on abstention}}\\
\rule{1.25em}{0pt}{\small Poulsen, S., Coronel, J. C., \textbf{Sweitzer, M. D.}, Bullock, O. M., Shulman, H. C., \& Bond, R. M.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small National Communication Association (NCA) Annual Convention} & {\small 2019}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Choice homophily in political discussion networks: Evidence from formal dynamic models of the selectivity function}}\\
\rule{1.25em}{0pt}{\small \textbf{Sweitzer, M. D.}}\vspace{0.5em}\\

\hangindent=1em \rule{1em}{0pt}{\raggedright \small \textit{Investigating how person-to-person communication transforms frames: A combined social transmission, content analysis, and eye movement monitoring approach} \textbf{(top paper)}}\\
\rule{1.25em}{0pt}{\small Coronel, J. C., Ott, J., \textbf{Sweitzer, M. D.}, Hubner, A., \& Lerner, S.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small International Communication Association (ICA) Annual Convention} & {\small 2019}\vspace{0.25em}\\
\hangindent=1em \rule{1em}{0pt}{\raggedright \small \textit{Using eye movements to determine when laboratory findings can be generalized to naturalistic settings: Linguistic features of messages and real-world voting behaviors}}\\
\rule{1.25em}{0pt}{\small Coronel, J. C., Bullock, O., Shulman, H. C., \textbf{Sweitzer, M. D.}, Bond, R. M., \& Poulsen, S.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small American Geophysical Union (AGU) Fall Meeting} & {\small 2018}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Evolution of water narratives in local U.S. newspapers}}\\
\rule{1.25em}{0pt}{\small Witte, A., Hornberger, G. M., Gunda, T., Gilligan, J., \& \textbf{Sweitzer, M. D.}}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small American Political Science Association (APSA) Annual Meeting} & {\small 2018}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Political homophily in a large-scale online communication network}}\\
\rule{1.25em}{0pt}{\small Bond, R. M., \& \textbf{Sweitzer, M. D.}}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small Association for Education in Journalism and Mass Communication (AEJMC) Annual Conference} & {\small 2018}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{More than a black and white issue: Racialized identity and support for Black Lives Matter}}\\
\rule{1.25em}{0pt}{\small Holt, L. F., \& \textbf{Sweitzer, M. D.}}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small International Communication Association (ICA) Annual Convention} & {\small 2018}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Political homophily in a large-scale online communication network}}\\
\rule{1.25em}{0pt}{\small Bond, R. M., \& \textbf{Sweitzer, M. D.}}\vspace{0.5em}\\

\rule{1em}{0pt}{\raggedright \small \textit{Down to a r/science: Integrating computational approaches to the study of communication on Reddit}}\\
\rule{1.25em}{0pt}{\small Bond, R. M., Hubner, A., McKnight, J., \& \textbf{Sweitzer, M. D.}}\vspace{0.5em}\\

\hangindent=1em \rule{1em}{0pt}{\raggedright \small \textit{The generation and spread of numerical misinformation: A combined eye movement and social transmission approach}}\\
\rule{1.25em}{0pt}{\small Coronel, J. C., Poulsen, S., \& \textbf{Sweitzer, M. D.}}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small National Communication Association (NCA) Annual Convention} & {\small 2017}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Survey of surveys: A content analysis of the language complexity in public opinion polls}}\\
\rule{1.25em}{0pt}{\small \textbf{Sweitzer, M. D.}, \& Shulman, H. C.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small Political Networks (PolNet) Conference} & {\small 2017}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Partisan network selection: Theoretical and agent-based models of homophilic political discussion networks}}\\
\rule{1.25em}{0pt}{\small \textbf{Sweitzer, M. D.}, \& Bond, R. M.}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small International Communication Association (ICA) Annual Convention} & {\small 2017}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Eye movements as measures of memory in communication research} \textbf{(top paper)}}\\
\rule{1.25em}{0pt}{\small Coronel, J. C., \& \textbf{Sweitzer, M. D.}}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small National Communication Association (NCA) Annual Convention} & {\small 2016}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Advancing framing theory: Using frames to improve public opinion via metacognition}}\\
\rule{1.25em}{0pt}{\small Shulman, H. C., \& \textbf{Sweitzer, M. D.}}
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\rule{0.5em}{0pt}{\small American Political Science Association (APSA) Annual Meeting} & {\small 2016}\vspace{0.25em}\\
\rule{1em}{0pt}{\raggedright \small \textit{Television news content predicts political knowledge}}\\
\rule{1.25em}{0pt}{\small \textbf{Sweitzer, M. D.}, \& Bond, R. M.}\vspace{0.5em}\\

\rule{1em}{0pt}{\raggedright \small \textit{Using structural topic models to assess television news content}}\\
\rule{1.25em}{0pt}{\small Bond, R. M., \& \textbf{Sweitzer, M. D.}}
\end{tabularx}

\vspace{1em}
{\large Research Grants}

\vspace{1em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Miller Research Award}, \$17,288.87 - Ohio State University, School of Communication & 2018\\
\rule{0.75em}{0pt}Principal Investigator: Jason Coronel
\end{tabularx}

\vspace{1em}
{\large Honors and Awards}

\vspace{1em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Walter Lippmann Best Article of the Year Award} & 2021\\
\rule{0.75em}{0pt}for ``Investigating the generation and spread of numerical misinformation''\\
\rule{0.75em}{0pt}American Political Science Association -- Political Communication Section
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Best Paper Award} for ``More than a black and white issue'' & 2020\\
\rule{0.75em}{0pt}The International Society for Self and Identity
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Doris Gildea Morgan Scholarship Award} (senior researcher award) & 2019\\
\rule{0.75em}{0pt}The Ohio State University School of Communication
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Top Paper Award} for ``Investigating how person-to-person communication transforms frames'' & 2019\\
\rule{0.75em}{0pt}National Communication Association -- Political Communication Division
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Walter B. Emery Memorial Scholarship Award} (junior researcher award) & 2018\\
\rule{0.75em}{0pt}The Ohio State University School of Communication
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Top Paper Award} for ``Eye movements as measures of memory in communication research'' & 2017\\
\rule{0.75em}{0pt}International Communication Association -- Communication, Science, \& Biology Division
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Travel Award} & 2017\\
\rule{0.75em}{0pt}International Communication Association -- Communication, Science, \& Biology Division
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Graduate Fellowship Award} & 2017\\
\rule{0.75em}{0pt}Political Networks Conference
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Honors Society Member} & 2011--\textit{present}\\
\rule{0.75em}{0pt}Lambda Pi Eta National Communication Honors Society, Chi Beta chapter
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Edward and Ellen Kniep Memorial Scholarship} & 2008 -- 2012\\
\rule{0.75em}{0pt}University of Missouri
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{John and Virginia Sutherland Scholarship} & 2008 -- 2012\\
\rule{0.75em}{0pt}University of Missouri
\end{tabularx}

\vspace{1em}
{\large Invited Talks}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Research Industry Career Opportunities after Grad School} & 2023\\
\rule{0.75em}{0pt}University of New Mexico -- Communication and Journalism Department
\end{tabularx}

\vspace{1em}
{\large Service}

\begin{itemize}
\item International Communication Association - Political Communication Division
\vspace{-10pt}
\begin{itemize}
\item \textit{Invited Reviewer} (Autumn 2017, 2018, 2019, 2020)
\end{itemize}
\item International Communication Association - Computational Methods Group
\vspace{-10pt}
\begin{itemize}
\item \textit{Invited Reviewer} (Autumn 2020)
\end{itemize}
\item National Communication Association - Political Communication Division
\vspace{-10pt}
\begin{itemize}
\item \textit{Invited Reviewer} (Spring 2018, 2019, 2020)
\end{itemize}
\item Ohio State University School of Communication
\vspace{-10pt}
\begin{itemize}
\item \textit{Peer Mentor} (Autumn 2018--Spring 2019)
\end{itemize}
\item Ohio State University School of Communication - Graduate Student Organization
\vspace{-10pt}
\begin{itemize}
\item \textit{Treasurer} (Autumn 2016--Summer 2017)
\end{itemize}
\end{itemize}

\vspace{0.3em}
{\large Additional Training}

\vspace{1em}
\begin{tabularx}{\textwidth}{Xr}
\textit{Machine Learning \& Deep Learning Workshops} & June 25 -- July 28, 2022\\
\rule{0.75em}{0pt}Sandia National Laboratories\vspace{0.5em}\\
\textit{Complex Systems Summer School} & June 10 -- July 6, 2018\\
\rule{0.75em}{0pt}Santa Fe Institute\vspace{0.5em}\\
\textit{Workshops on social network analysis} & June 14 -- 15, 2017\\
\rule{0.75em}{0pt}Political Networks Conference\vspace{0.5em}\\
\textit{Workshops on structural equation modeling} & August 8 -- 9, 2016\\
\rule{0.75em}{0pt}Statistical Horizons and The Ohio State University, School of Communication\vspace{0.5em}\\
\textit{Graduate teaching workshops} & August 15 -- 17, 2015\\
\rule{0.75em}{0pt}The Ohio State University, University Center for the Advancement of Teaching\\
\end{tabularx}

\vspace{1em}
{\large Academic Appointments}

\begin{itemize}
\item The Ohio State University
\end{itemize}

\begin{tabularx}{\textwidth}{lXr}
&Teaching\vspace{0.25em}\\
&\rule{1em}{0pt}\textit{Social Media} -- Instructor of Record & Summer 2021\rule{2em}{0pt}\\
&\rule{2em}{0pt}{\small no evaluation data}\vspace{.25em}\\
&\rule{1em}{0pt}\textit{Communication Industry Research Methods} -- Laboratory Instructor & Spring 2021\rule{2em}{0pt}\\
&\rule{2em}{0pt}{\small \textit{Dr. Jason Coronel}; Student evaluation: 5.00/5}\vspace{.25em}\\
&\rule{1em}{0pt}\textit{Communication Industry Research Methods} -- Laboratory Instructor & Fall 2020\rule{2em}{0pt}\\
&\rule{2em}{0pt}{\small \textit{Dr. Jason Coronel}; Student evaluation: 4.44/5}\vspace{.25em}\\
&\rule{1em}{0pt}\textit{Communication Industry Research Methods} -- Instructor of Record & Summer 2020\rule{2em}{0pt}\\
&\rule{2em}{0pt}{\small Student evaluation: 4.64/5}\vspace{.25em}\\
&\rule{1em}{0pt}\textit{Communication Industry Research Methods} -- Laboratory Instructor & Spring 2019\rule{2em}{0pt}\\
&\rule{2em}{0pt}{\small \textit{Dr. Olga Kamenchuk}; Student evaluation: 4.67/5}\vspace{.25em}\\
&\rule{1em}{0pt}\textit{Communication Industry Research Methods} -- Laboratory Instructor & Fall 2018\rule{2em}{0pt}\\
&\rule{2em}{0pt}{\small \textit{Dr. Olga Kamenchuk}; Student evaluation: 4.05/5}\vspace{.25em}\\
&\rule{1em}{0pt}\textit{Persuasive Communication} -- Instructor of Record & Spring 2016\rule{2em}{0pt}\\
&\rule{2em}{0pt}{\small Student evaluation: 4.74/5}\vspace{.25em}\\
&\rule{1em}{0pt}\textit{Crisis Communication} -- Teaching Assistant & Fall 2015\rule{2em}{0pt}\\
&\rule{2em}{0pt}{\small \textit{Dr. Lanier Holt}; no evaluation data}\\
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{lXr}
&Graduate Research Associate\vspace{0.25em}\\
&\rule{1em}{0pt}\textit{Dr. Robert Bond} & Fall 2016 -- Summer 2017, Spring 2020\rule{2em}{0pt}\vspace{.125em}\\
&\rule{1em}{0pt}\textit{Dr. David DeAndrea} & Fall 2019\rule{2em}{0pt}\vspace{.125em}\\
&\rule{1em}{0pt}\textit{Dr. Lanier Holt} & Fall 2017 -- Spring 2018\rule{2em}{0pt}\vspace{.125em}\\
&\rule{1em}{0pt}\textit{Dr. Jason Coronel} & Summer 2016, Summer 2018\rule{2em}{0pt}\\
\end{tabularx}

\vspace{1em}
{\large Professional Memberships}

\vspace{1em}
\begin{tabularx}{\textwidth}{Xr}
International Society for Computational Social Science (ISCSS) & Member, 2022 -- \textit{present}\vspace{0.5em}\\
International Communication Association (ICA) & Member, 2017 -- \textit{present}\vspace{0.5em}\\
National Communication Association (NCA) & Member, 2016 -- \textit{present}\vspace{0.5em}\\
American Political Science Association (APSA) & Member, 2016 -- \textit{present}\vspace{0.5em}\\
\end{tabularx}

%\vspace{1em}
\pagebreak
{\large Professional References}

\vspace{0.5em}
\begin{center}
\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
{Dr. Thushara Gunda} & Dr. Asmeret Naugle\\
Sandia National Laboratories & Sandia National Laboratories\\
\href{mailto:tgunda@sandia.gov}{tgunda@sandia.gov} & \href{mailto:abier@sandia.gov}{abier@sandia.gov}\\
\\
{Dr. Robert Bond (advisor)} & {Dr. Hillary Shulman (committee)}\\
School of Communication & School of Communication\\
The Ohio State University & The Ohio State University\\
\href{mailto:bond.136@osu.edu}{bond.136@osu.edu} & \href{mailto:shulman.36@osu.edu}{shulman.36@osu.edu}\\
\\
{Dr. William Eveland, Jr. (committee)} & {Dr. Jason Coronel}\\
School of Communication & School of Communication\\
The Ohio State University & The Ohio State University\\
\href{mailto:eveland.6@osu.edu}{eveland.6@osu.edu} & \href{mailto:coronel.4@osu.edu}{coronel.4@osu.edu}
\end{tabular}
\end{center}
\end{document}
