\documentclass[letterpaper, 9pt]{extarticle}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcolumntype{Z}{>{\flushright\arraybackslash}X}

\usepackage[T1]{fontenc}

\def\name{Matthew D. Sweitzer, Ph.D.}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Résumé},
  pdfsubject = {Résumé},
  pdfpagemode = UseNone
}

\geometry{
  body={7.5in, 10in},
  left=0.5in,
  top=0.5in
}

\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

\setlength\parindent{0pt}

\usepackage{enumitem}

\begin{document}
{\fontfamily{qpl}\selectfont
\begin{center}
{\Large \bf \name}
\end{center}

\vspace{0pt}

\begin{tabularx}{\textwidth}{lXr}
Phone: & (815) 307-2647\\% & Mail:\\
Email: & \href{mailto:email@mattsweitzer.com}{email@mattsweitzer.com}\\% & 4337 N College Ave.\\
Homepage: & \href{https://mattsweitzer.com}{https://mattsweitzer.com}\\% & Indianapolis, IN 46205\\
\end{tabularx}

\vspace{0pt}

\rule{\textwidth}{0.25pt}
\raggedright

\vspace{-4pt}
\begin{center}
\large{Qualifications}
\end{center}

\begin{itemize}[leftmargin=!,labelindent=-10pt,itemindent=0pt]
\item Proficient in Python, \textit{R}, Rust, Javascript, HTML, CSS, \LaTeX , and SQL computing languages, as well as distributed batch scheduling on supercomputers with Slurm and Torque.

\vspace{-4pt}
\item Designed, implemented, analyzed, and published computational social scientific research using a variety of methods, including machine learning, cross-sectional and longitudinal social network analysis, natural language processing, structural equation modeling, bayesian statistics, and maximum likelihood estimation.

\vspace{-4pt}
\item History of taking on complex responsibilities, communicating with diverse and interdisciplinary team members, and managing multiple projects and teams, in both academic and industry research settings.
\end{itemize}

\vspace{-7.5pt}

\rule{\textwidth}{0.25pt}
\raggedright

\vspace{-4pt}
\begin{center}
\large{Education}
\end{center}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
OHIO STATE UNIVERSITY & OHIO STATE UNIVERSITY & UNIVERSITY OF MISSOURI\\
Ph.D., Communication & M.A., Communication & B.A. (Honors), Communication\\
\textit{Graduated July 2021} & \textit{Graduated May 2019} & \textit{Graduated May 2012}\\
\end{tabular*}

\vspace{7.5pt}

\rule{\textwidth}{0.25pt}
\raggedright

\vspace{-4pt}
\begin{center}
\large{Recent Employment History}
\end{center}

SANDIA NATIONAL LABORATORIES, Machine Intelligence and Visualization -- Albuquerque, NM

\begin{tabularx}{\textwidth}{Xr}
\textbf{Senior Member of Technical Staff} & September, 2022 -- \textit{present}\\
\textbf{Postdoctoral Appointee} & July, 2021 -- September, 2022\\
\textbf{Graduate Technical Intern} & May, 2019 -- July, 2021
\end{tabularx}

\vspace{-4pt}
\begin{itemize}[leftmargin=!,labelindent=5pt,itemindent=0pt]
\item Served as work package manager on a machine learning project with direct reports at the U.S. Department of Energy.

\vspace{-6pt}
\item  Led the development and testing of new network analytic measures and their predictive capacity of social group stability in machine learning models.

\vspace{-6pt}
\item  Developed machine learning and natural language processing data analytic pipelines across different projects and programming languages.
\end{itemize}

OHIO STATE UNIVERSITY, School of Communication -- Columbus, OH
\begin{tabularx}{\textwidth}{Xr}
\textbf{Graduate Research \& Teaching Associate} & August, 2015 -- July, 2021
\end{tabularx}

\vspace{-4pt}
\begin{itemize}[leftmargin=!,labelindent=5pt,itemindent=0pt]
\item  Designed, implemented, analyzed data, and presented results for several social-scientific studies involving a wide variety of methods and procedures.

\vspace{-6pt}
\item  Trained and managed other graduate and undergraduate research assistants.

\vspace{-6pt}
\item  Contributed to a successful application for a research grant (Miller Award, see full CV on my website).

\vspace{-6pt}
\item  Independently taught industry research methods, social media, and persuasive communication courses.

\vspace{-6pt}
\item  Assisted in the instruction of crisis communication and industry research methods, including guest lectures.

\vspace{-6pt}
\item  Crafted and graded assignments, including examples of research designs and data analyses.
\end{itemize}

\vspace{-7.5pt}

\rule{\textwidth}{0.25pt}
\raggedright

\vspace{-4pt}
\begin{center}
\large{Additional Training}
\end{center}

\begin{itemize}[leftmargin=!,labelindent=-10pt,itemindent=0pt]
\item \textit{Machine Learning \& Deep Learning Workshop}, Sandia National Laboratories, July 25 -- 28, 2022

\vspace{-6pt}
\item \textit{Complex Systems Summer School}, Santa Fe Institute, June 10 -- July 6, 2018

\vspace{-6pt}
\item \textit{Workshops on Social Network Analysis}, Political Networks Conference, June 14 -- 15, 2017

\vspace{-6pt}
\item \textit{Statistical Horizons -- Structural Equation Modeling}, The Ohio State University, August 8 -- 9, 2016
\end{itemize}

\vspace{-7.5pt}

\rule{\textwidth}{0.25pt}
\raggedright

\vspace{-4pt}
\begin{center}
\large{Additional Accomplishments and Awards}
\end{center}

\begin{itemize}[leftmargin=!,labelindent=-10pt,itemindent=0pt]
\item Published 28 articles across top-ranked, peer-reviewed academic journals and conference proceedings.

\vspace{-6pt}
\item Presented numerous projects at academic conferences in the social sciences, complexity science, military and government research, and nuclear research fields.

\vspace{-6pt}
\item Won five top paper awards from the International Communication Association, the National Communication Association, the American Political Science Association, and the International Society for Self and Identity.

\vspace{-6pt}
\item \textit{Doris Gildea Morgan Scholarship} (senior researcher of the year) - Ohio State University, School of Communication (Awarded 2019)

\vspace{-6pt}
\item \textit{Walter B. Emery Memorial Scholarship} (junior researcher of the year) - Ohio State University, School of Communication (Awarded 2018)

\vspace{-6pt}
\item \textit{2017 Graduate Fellowship Award} - Political Networks Conference

\vspace{-6pt}
\item \textit{Member} -- Lambda Pi Eta National Communication Honors Society, Chi Beta chapter

\vspace{-6pt}
\item \textit{Edward and Ellen Kniep Memorial Scholarship} -- University of Missouri (Awarded 2008-2012)

\vspace{-6pt}
\item \textit{John and Virginia Sutherland Scholarship} -- University of Missouri (Awarded 2008-2012)
\end{itemize}

\vspace{-10pt}

\rule{\textwidth}{0.25pt}
}\end{document}